---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Between Subjects Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASIalt)
```

# Estimation Approach to Statistical Inference
## Between Subjects Vignette

### Three Group Example Data

```{r}
Group <- c(rep(1,3),rep(2,3),rep(3,3))
Outcome <- c(3,4,5,7,8,9,8,9,10)
Group <- factor(Group,levels=c(1,2,3),labels=c("Group1","Group2","Group3"))

BetweenData <- data.frame(Group,Outcome)
BetweenData
```

### Analyses of Multiple Groups

#### Confidence Intervals for the Means

```{r}
.ciMeans(Outcome~Group)
.ciMeans(Outcome~Group,conf.level=.99)
```

#### Plot of the Confidence Intervals for the Means

```{r,Between-Means}
.cipMeans(Outcome~Group)
.cipMeans(Outcome~Group,conf.level=.99,mu=5)
```

#### Significance Tests for the Means

```{r}
.nhstMeans(Outcome~Group)
.nhstMeans(Outcome~Group,mu=5)
```

### Analyses of a Group Comparison

#### Confidence Interval for a Mean Difference

```{r}
Comparison=factor(Group,c("Group1","Group2"))
.ciDifference(Outcome~Comparison)
.ciDifference(Outcome~Comparison,conf.level=.99)
Comparison=factor(Group,c("Group3","Group1"))
.ciDifference(Outcome~Comparison)
```

#### Plot of the Confidence Interval for the Mean Difference

```{r,Between-Difference}
Comparison=factor(Group,c("Group1","Group2"))
.cipDifference(Outcome~Comparison)
.cipDifference(Outcome~Comparison,conf.level=.99)
```

#### Significance Test of the Mean Difference

```{r}
.nhstDifference(Outcome~Comparison)
.nhstDifference(Outcome~Comparison,mu=2)
```

### Analyses of Pairwise Comparisons

#### Confidence Intervals for the Pairwise Comparisons

```{r}
.ciPairwise(Outcome~Group)
.ciPairwise(Outcome~Group,conf.level=.99)
```

#### Plot of the Confidence Intervals for the Pairwise Comparisons

```{r,Between-Pairwise}
.cipPairwise(Outcome~Group)
.cipPairwise(Outcome~Group,mu=-2,conf.level=.99)
```

#### Significance Tests of the Pairwise Comparisons

```{r}
.nhstPairwise(Outcome~Group)
.nhstPairwise(Outcome~Group,mu=-2)
```

### Analyses of a Set of Contrasts

#### Confidence Intervals for the Set of Contrasts

```{r}
.ciContrasts(Outcome~Group,contrasts=contr.sum)
.ciContrasts(Outcome~Group,contrasts=contr.sum,conf.level=.99)

.ciContrasts(Outcome~Group,contrasts=contr.treatment)
.ciContrasts(Outcome~Group,contrasts=contr.poly)
.ciContrasts(Outcome~Group,contrasts=contr.helmert)
.ciContrasts(Outcome~Group,contrasts=contr.SAS)
```

#### Plot of the Confidence Intervals for the Set of Contrasts

```{r,Between-Contrasts}
.cipContrasts(Outcome~Group,contrasts=contr.sum)
.cipContrasts(Outcome~Group,contrasts=contr.sum,conf.level=.99)

.cipContrasts(Outcome~Group,contrasts=contr.treatment)
.cipContrasts(Outcome~Group,contrasts=contr.poly)
.cipContrasts(Outcome~Group,contrasts=contr.helmert)
.cipContrasts(Outcome~Group,contrasts=contr.SAS)
```

#### Significance Tests of the Set of Contrasts

```{r}
.nhstContrasts(Outcome~Group,contrasts=contr.sum)
.nhstContrasts(Outcome~Group,contrasts=contr.treatment)
.nhstContrasts(Outcome~Group,contrasts=contr.poly)
.nhstContrasts(Outcome~Group,contrasts=contr.helmert)
.nhstContrasts(Outcome~Group,contrasts=contr.SAS)
```
