---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Repeated Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASIalt)
```

# Estimation Approach to Statistical Inference
## Repeated Vignette

### Contents

- [Data Management](#data-management)
- [Analyses of a Model](#analyses-of-a-model)
- [Analyses of the Variable Means](#analyses-of-the-variable-means)
- [Analyses of a Variable Comparison](#analyses-of-a-variable-comparison)
- [Analyses of Pairwise Comparisons](#analyses-of-pairwise-comparisons)
- [Analyses of a Set of Contrasts](#analyses-of-a-set-of-contrasts)

### Data Management

#### Data Entry

```{r}
Outcome1 <- c(0,0,3,5)
Outcome2 <- c(4,7,4,9)
Outcome3 <- c(9,6,4,9)
RepeatedData <- data.frame(Outcome1,Outcome2,Outcome3)
```

#### Inspect Data

```{r,Repeated-Data}
RepeatedData
describeBoxes(Outcome1,Outcome2,Outcome3)
plotBoxes(Outcome1,Outcome2,Outcome3)
addData(Outcome1,Outcome2,Outcome3)
```

#### Descriptive Statistics

```{r}
describeMeans(Outcome1,Outcome2,Outcome3)
```

### Analyses of a Model

#### Describe a Model

```{r}
describeModel(Outcome1,Outcome2,Outcome3)
```

#### Overall Fit of a Model

```{r}
fitModel(Outcome1,Outcome2,Outcome3)
```

#### Significance Test of a Model

```{r}
testModel(Outcome1,Outcome2,Outcome3)
```

### Analyses of the Variable Means

#### Confidence Intervals for the Means

```{r}
estimateMeans(Outcome1,Outcome2,Outcome3)
estimateMeans(Outcome1,Outcome2,Outcome3,conf.level=.99)
```

#### Plots of Confidence Intervals for the Means

```{r,Repeated-Means}
plotMeans(Outcome1,Outcome2,Outcome3)
plotMeans(Outcome1,Outcome2,Outcome3,conf.level=.99,mu=5)
```

#### Significance Tests for the Means

```{r}
testMeans(Outcome1,Outcome2,Outcome3)
testMeans(Outcome1,Outcome2,Outcome3,mu=5)
```

### Analyses of a Variable Comparison

#### Confidence Interval for the Mean Difference

```{r}
estimateDifference(Outcome1,Outcome2)
estimateDifference(Outcome1,Outcome2,conf.level=.99)
estimateDifference(Outcome3,Outcome1)
```

#### Plots of Confidence Intervals for the Mean Difference

```{r,Repeated-Difference}
plotDifference(Outcome1,Outcome2)
plotDifference(Outcome1,Outcome2,conf.level=.99)
```

#### Significance Test for the Mean Difference

```{r}
testDifference(Outcome1,Outcome2)
testDifference(Outcome1,Outcome2,mu=-2)
```

### Analyses of Pairwise Comparisons

#### Confidence Intervals for the Pairwise Comparisons

```{r}
estimatePairwise(Outcome1,Outcome2,Outcome3)
estimatePairwise(Outcome1,Outcome2,Outcome3,conf.level=.99)
```

#### Plot of the Confidence Intervals for the Pairwise Comparisons

```{r,Repeated-Pairwise}
plotPairwise(Outcome1,Outcome2,Outcome3)
plotPairwise(Outcome1,Outcome2,Outcome3,mu=-2,conf.level=.99)
```

#### Significance Tests of the Pairwise Comparisons

```{r}
testPairwise(Outcome1,Outcome2,Outcome3)
testPairwise(Outcome1,Outcome2,Outcome3,mu=-2)
```

### Analyses of a Set of Contrasts

#### Confidence Intervals for the Set of Contrasts

```{r}
estimateContrasts(Outcome1,Outcome2,Outcome3,contrasts=contr.sum)
estimateContrasts(Outcome1,Outcome2,Outcome3,contrasts=contr.sum,conf.level=.99)

estimateContrasts(Outcome1,Outcome2,Outcome3,contrasts=contr.treatment)
estimateContrasts(Outcome1,Outcome2,Outcome3,contrasts=contr.poly)
estimateContrasts(Outcome1,Outcome2,Outcome3,contrasts=contr.helmert)
estimateContrasts(Outcome1,Outcome2,Outcome3,contrasts=contr.SAS)
```

#### Plot of the Confidence Intervals for the Set of Contrasts

```{r,Repeated-Contrasts}
plotContrasts(Outcome1,Outcome2,Outcome3,contrasts=contr.sum)
plotContrasts(Outcome1,Outcome2,Outcome3,contrasts=contr.sum,conf.level=.99)

plotContrasts(Outcome1,Outcome2,Outcome3,contrasts=contr.treatment)
plotContrasts(Outcome1,Outcome2,Outcome3,contrasts=contr.poly)
plotContrasts(Outcome1,Outcome2,Outcome3,contrasts=contr.helmert)
plotContrasts(Outcome1,Outcome2,Outcome3,contrasts=contr.SAS)
```

#### Significance Tests of the Set of Contrasts

```{r}
testContrasts(Outcome1,Outcome2,Outcome3,contrasts=contr.sum)
testContrasts(Outcome1,Outcome2,Outcome3,contrasts=contr.treatment)
testContrasts(Outcome1,Outcome2,Outcome3,contrasts=contr.poly)
testContrasts(Outcome1,Outcome2,Outcome3,contrasts=contr.helmert)
testContrasts(Outcome1,Outcome2,Outcome3,contrasts=contr.SAS)
```
