---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{OneWay Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASIalt)
```

# Estimation Approach to Statistical Inference
## OneWay Vignette

### Contents

- [Data Management](#data-management)
- [Analyses of a Model](#analyses-of-a-model)
- [Analyses of the Factor Means](#analyses-of-the-factor-means)
- [Analyses of a Factor Comparison](#analyses-of-a-factor-comparison)
- [Analyses of Pairwise Comparisons](#analyses-of-pairwise-comparisons)
- [Analyses of a Set of Contrasts](#analyses-of-a-set-of-contrasts)

### Data Management

#### Data Entry

```{r}
Factor <- c(rep(1,4),rep(2,4),rep(3,4))
Outcome <- c(0,0,3,5,4,7,4,9,9,6,4,9)
Factor <- factor(Factor,levels=c(1,2,3),labels=c("Level1","Level2","Level3"))
OneWayData <- data.frame(Factor,Outcome)
```

#### Inspect Data

```{r,OneWay-Data}
OneWayData
describeBoxes(Outcome~Factor)
plotBoxes(Outcome~Factor)
addData(Outcome~Factor)
```

#### Descriptive Statistics

```{r}
describeMeans(Outcome~Factor)
```

### Analyses of a Model

#### Describe a Model

```{r}
describeModel(Outcome~Factor)
```

#### Overall Fit of a Model

```{r}
fitModel(Outcome~Factor)
```

#### Significance Test of a Model

```{r}
testModel(Outcome~Factor)
```

### Analyses of the Factor Means

#### Confidence Intervals for the Means

```{r}
estimateMeans(Outcome~Factor)
estimateMeans(Outcome~Factor,conf.level=.99)
```

#### Plot of the Confidence Intervals for the Means

```{r,OneWay-Means}
plotMeans(Outcome~Factor)
plotMeans(Outcome~Factor,conf.level=.99,mu=5)
```

#### Significance Tests for the Means

```{r}
testMeans(Outcome~Factor)
testMeans(Outcome~Factor,mu=5)
```

### Analyses of a Factor Comparison

#### Confidence Interval for a Mean Difference

```{r}
Comparison=factor(Factor,c("Level1","Level2"))
estimateDifference(Outcome~Comparison)
estimateDifference(Outcome~Comparison,conf.level=.99)
Comparison=factor(Factor,c("Level3","Level1"))
estimateDifference(Outcome~Comparison)
```

#### Plot of the Confidence Interval for the Mean Difference

```{r,OneWay-Difference}
Comparison=factor(Factor,c("Level1","Level2"))
plotDifference(Outcome~Comparison)
plotDifference(Outcome~Comparison,conf.level=.99)
```

#### Significance Test of the Mean Difference

```{r}
testDifference(Outcome~Comparison)
testDifference(Outcome~Comparison,mu=-2)
```

### Analyses of Pairwise Comparisons

#### Confidence Intervals for the Pairwise Comparisons

```{r}
estimatePairwise(Outcome~Factor)
estimatePairwise(Outcome~Factor,conf.level=.99)
```

#### Plot of the Confidence Intervals for the Pairwise Comparisons

```{r,OneWay-Pairwise}
plotPairwise(Outcome~Factor)
plotPairwise(Outcome~Factor,mu=-2,conf.level=.99)
```

#### Significance Tests of the Pairwise Comparisons

```{r}
testPairwise(Outcome~Factor)
testPairwise(Outcome~Factor,mu=-2)
```

### Analyses of a Set of Contrasts

#### Confidence Intervals for the Set of Contrasts

```{r}
estimateContrasts(Outcome~Factor,contrasts=contr.sum)
estimateContrasts(Outcome~Factor,contrasts=contr.sum,conf.level=.99)

estimateContrasts(Outcome~Factor,contrasts=contr.treatment)
estimateContrasts(Outcome~Factor,contrasts=contr.poly)
estimateContrasts(Outcome~Factor,contrasts=contr.helmert)
estimateContrasts(Outcome~Factor,contrasts=contr.SAS)
```

#### Plot of the Confidence Intervals for the Set of Contrasts

```{r,OneWay-Contrasts}
plotContrasts(Outcome~Factor,contrasts=contr.sum)
plotContrasts(Outcome~Factor,contrasts=contr.sum,conf.level=.99)

plotContrasts(Outcome~Factor,contrasts=contr.treatment)
plotContrasts(Outcome~Factor,contrasts=contr.poly)
plotContrasts(Outcome~Factor,contrasts=contr.helmert)
plotContrasts(Outcome~Factor,contrasts=contr.SAS)
```

#### Significance Tests of the Set of Contrasts

```{r}
testContrasts(Outcome~Factor,contrasts=contr.sum)
testContrasts(Outcome~Factor,contrasts=contr.treatment)
testContrasts(Outcome~Factor,contrasts=contr.poly)
testContrasts(Outcome~Factor,contrasts=contr.helmert)
testContrasts(Outcome~Factor,contrasts=contr.SAS)
```
