---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Regression Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASIalt)
```

# Estimation Approach to Statistical Inference
## Regression Vignette

## Contents

- [Data Management](#data-management)
- [Analyses of a Regression Model](#analyses-of-a-regression-model)
- [Analyses of the Regression Coefficients](#analyses-of-the-regression-coefficients)

### Data Management

#### Data Entry

```{r}
Predictor1 <- c(0,0,3,5)
Predictor2 <- c(4,7,4,9)
Criterion <- c(9,6,4,9)
RegressionData <- data.frame(Predictor1,Predictor2,Criterion)
```

#### Inspect Data

```{r,Regression-Data}
RegressionData
describeBoxes(Predictor1,Predictor2)
plotBoxes(Predictor1,Predictor2)
addData(Predictor1,Predictor2)
describeBoxes(Criterion)
plotBoxes(Criterion)
addData(Criterion)
```

#### Descriptive Statistics

```{r}
describeMeans(Predictor1,Predictor2,Criterion)
```

### Analyses of a Regression Model

#### Overall Fit of Regression Model

```{r}
describeModel(Criterion~Predictor1+Predictor2)
```

#### Significance Test of the Regression Model

```{r}
testModel(Criterion~Predictor1+Predictor2)
```

### Analyses of the Regression Coefficients

#### Confidence Intervals for the Regression Coefficients

```{r}
estimateRegression(Criterion~Predictor1+Predictor2)
estimateRegression(Criterion~Predictor1+Predictor2,conf.level=.99)
```

#### Plot of the Confidence Intervals for the Regression Coefficients

```{r,Regression-Coefficients}
plotRegression(Criterion~Predictor1+Predictor2)
plotRegression(Criterion~Predictor1+Predictor2,conf.level=.99)
```

#### Significance Tests for the Regression Coefficients

```{r}
testRegression(Criterion~Predictor1+Predictor2)
```
