---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Within Subjects Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASIalt)
```

# Estimation Approach to Statistical Inference
## Within Subjects Vignette

### Data Management

#### Data Entry

```{r}
Time1 <- c(5,6,6,7,8)
Time2 <- c(7,7,8,8,9)
Time3 <- c(8,8,9,9,9)
WithinData <- data.frame(Time1,Time2,Time3)
```

#### Inspect Data

```{r,Within-Data}
WithinData
plotData(Time1,Time2,Time3)
```

#### Descriptive Statistics

```{r}
describeMeans(Time1,Time2,Time3)
```

### Analyses of a Model

#### Overall Fit of a Model

```{r}
effectModel(Time1,Time2,Time3)
```

#### Significance Test of a Model

```{r}
testModel(Time1,Time2,Time3)
```

### Analyses of the Variable Means

#### Confidence Intervals for the Means

```{r}
estimateMeans(Time1,Time2,Time3)
estimateMeans(Time1,Time2,Time3,conf.level=.99)
```

#### Plots of Confidence Intervals for the Means

```{r,Within-Means}
plotMeans(Time1,Time2,Time3)
plotMeans(Time1,Time2,Time3,conf.level=.99,mu=6)
```

#### Significance Tests for the Means

```{r}
testMeans(Time1,Time2,Time3)
testMeans(Time1,Time2,Time3,mu=6)
```

### Analyses of a Variable Comparison

#### Confidence Interval for the Mean Difference

```{r}
estimateDifference(Time1,Time2)
estimateDifference(Time1,Time2,conf.level=.99)
estimateDifference(Time3,Time1)
```

#### Plots of Confidence Intervals for the Mean Difference

```{r,Within-Difference}
plotDifference(Time1,Time2)
plotDifference(Time1,Time2,conf.level=.99)
```

#### Significance Test for the Mean Difference

```{r}
testDifference(Time1,Time2)
testDifference(Time1,Time2,mu=-2)
```

### Analyses of Pairwise Comparisons

#### Confidence Intervals for the Pairwise Comparisons

```{r}
estimatePairwise(Time1,Time2,Time3)
estimatePairwise(Time1,Time2,Time3,conf.level=.99)
```

#### Plot of the Confidence Intervals for the Pairwise Comparisons

```{r,Within-Pairwise}
plotPairwise(Time1,Time2,Time3)
plotPairwise(Time1,Time2,Time3,mu=-2,conf.level=.99)
```

#### Significance Tests of the Pairwise Comparisons

```{r}
testPairwise(Time1,Time2,Time3)
testPairwise(Time1,Time2,Time3,mu=-2)
```

### Analyses of a Set of Contrasts

#### Confidence Intervals for the Set of Contrasts

```{r}
estimateContrasts(Time1,Time2,Time3,contrasts=contr.sum)
estimateContrasts(Time1,Time2,Time3,contrasts=contr.sum,conf.level=.99)

estimateContrasts(Time1,Time2,Time3,contrasts=contr.treatment)
estimateContrasts(Time1,Time2,Time3,contrasts=contr.poly)
estimateContrasts(Time1,Time2,Time3,contrasts=contr.helmert)
estimateContrasts(Time1,Time2,Time3,contrasts=contr.SAS)
```

#### Plot of the Confidence Intervals for the Set of Contrasts

```{r,Within-Contrasts}
plotContrasts(Time1,Time2,Time3,contrasts=contr.sum)
plotContrasts(Time1,Time2,Time3,contrasts=contr.sum,conf.level=.99)

plotContrasts(Time1,Time2,Time3,contrasts=contr.treatment)
plotContrasts(Time1,Time2,Time3,contrasts=contr.poly)
plotContrasts(Time1,Time2,Time3,contrasts=contr.helmert)
plotContrasts(Time1,Time2,Time3,contrasts=contr.SAS)
```

#### Significance Tests of the Set of Contrasts

```{r}
testContrasts(Time1,Time2,Time3,contrasts=contr.sum)
testContrasts(Time1,Time2,Time3,contrasts=contr.treatment)
testContrasts(Time1,Time2,Time3,contrasts=contr.poly)
testContrasts(Time1,Time2,Time3,contrasts=contr.helmert)
testContrasts(Time1,Time2,Time3,contrasts=contr.SAS)
```
